---
title: "Nino Publications"
author: "Daniel Foley"
date: "07/06/2019"
output:
  govdown::govdown_document:
    font: "sans-serif" # (default) or "new-transport"
    favicon: "govuk"
    logo: "images/govdown-logo-white-on-transparent.svg"
    logo_url: "https://ukgovdatascience.github.io/govdown"
    logo_text:  "DWP" 
    page_title: "Nino Publications"
    title: "Department for Work and Pensions Statistics"
    phase: alpha
    feedback_url: "https://github.com/ukgovdatascience/govdown/issues"
    google_analytics: "UA-12345678-90"
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# rmarkdown::render("Nino_main_page.Rmd")
```


```{r }
data <- eu_non_eu_total("2002-03-01", "2018-12-01", "quarter")
year_to_date = "Dec"
year_end_filter = "quarter_dates"
country_labels = c("European_Union_EU15","European_Union_EU2", "European_Union_EU8", "Oceania",
           "Central_and_South_America", "North_America", "North_Africa", "Sub_Saharan_Africa",
           "South_East_Asia", "South_Asia", "East_Asia", "Middle_East_and_Central_Asia")
labels = c("European_Union_EU15","European_Union_EU2", "European_Union_EU8")
```



What do these statistics show? A National Insurance Number (NINo) is generally required by any adult overseas national looking to work or claim benefits / tax credits in
the UK. As such they show a count, by individual nationality, of the number of NINos registered to adult non-UK nationals each quarter, irrespective of the length of stay in
the UK. The NINo statistics are not a count of the number of adult non-UK nationals currently residing in the UK


## Main stories

### 633 thousand NINos registered in the year to
December 2018: a 7% decrease on the previous year


```{r fig.width=14, fig.height=7}
create_figure_1(data, "Sep", FALSE, TRUE)
```

The increase in registrations seen in the last two quarters of the year to March 2019 are likely to reflect
the processing of pending applications and increased operational activity resulting from the opening of
two new processing centres.


```{css echo=FALSE}

}
```

$~$

In the year to December 2018, 66% are
from within the EU.


$~$

<center>

```{r fig.width=6, fig.height=6}

create_figure_2(data, year_to_date, FALSE, TRUE)
```
</center>

$~$


## Where in the world are people registering from?

#### Registrations to EU nationals have continued to fall.

In the year to December 2018, there were 419,000 NINo
registrations by EU nationals (down 16% on the previous year).

Registrations across all EU sub groups have decreased:
- EU15 down 14% to 162,000
- EU8 down 25% to 85,000
- EU2 down 13% to 168,000

Registrations to EU8 nationals now account for 20% of all EU
registrations, this is down from 74% in 2007.

Note: There was a sharp rise in NINo registrations in 2014 following the
removal of restrictions on work for EU2 citizens. Some of this is reflecting
individuals who were residing in the UK prior 2014 and would only have been
able to register for a NINo after that date (see arrival to registration analysis
on EU2 nationals).

 - Registrations to EU8 nationals now account for 19% of all EU
registrations, this is down from 74% in 2007.


- In the year to March 2019 registrations to non-EU national increased by
17%, to 226,000. 58% of this increase was contributed by the increase
of registrations to Indian nationals.


```{r fig.width=14, fig.height=7}
create_figure_3(data, year_to_date, year_end_filter, labels, FALSE, TRUE)
```


$~$

## Outside of the EU, South Asia has the most registrations

```{r fig.width=14, fig.height=7}
create_figure_4(data, year_to_date, country_labels, FALSE, TRUE)
```


